---
title: "Statistical report for ACASA-TAVI"
author: "C. Cunen"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output: 
  #bookdown::html_document2:
  #  toc: true
  #  toc_depth: '2'
  word_document:
    number_sections: true
    toc: true
    toc_depth: '2'
  #pdf_document:
  #  toc: true
  #  toc_depth: '2'
  #html_document:
  #  toc: true
  #  toc_depth: 2
  #  number_sections: true
subtitle: AntiCoagulation versus AcetylSalicylic Acid after Transcatheter Aortic Valve Implantation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(knitr) #for tables
library(flextable) # for nice tables
library(broom) # for tidy function 
library(ggpubr) # for plots with combined panels

options(tidyverse.quiet = TRUE) # suppress package loading messages
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) #to set the working directory back to the folder containing the .Rproj file during knitting
```

```{r, message = TRUE}
rm(list = ls())

#datafile = '../data/raw/UiO_20250821_115105.xlsx'
#treatment_file = '../data/raw/2025-08-20 BASIC avblinding.xlsx'
#if (grepl('Fake', treatment_file, fixed = TRUE) == TRUE | grepl('fake', treatment_file, fixed = TRUE) == TRUE) {
#print('We are using a fake allocation list!')
#}

```

```{r, message = FALSE, warning=FALSE}
#source('../Rcode/raw_to_td.R')
#source('../Rcode/tables_descriptive.R') # a script with many tables
#source('../Rcode/raw-to-ad.R')
load("data/res/disp_tab.RData")
load("data/res/baseline_tab.RData")
```

# Introduction

The ACASA-TAVI study is a two-arm, randomised, controlled, parallel-group, multicentre, single-country, open-label blinded-endpoint, Phase III trial. Patients are randomised to either ASA (usual care) or DOAC (active treatment) in a 1:1 ratio. The goal of the study is to evaluate the efficacy and safety of DOAC versus ASA after TAVI. Treatment duration is 12 months and the primary endpoints are evaluated at 12 months. See Protocol (current version is dated November 10th 2022).

This report summarises the results from the analysis of primary and secondary endpoints, as well as baseline and safety data. 

All 360 randomised patients are included in all analyses (except in some sensitivity analyses, where this is made explicit). The analyses have been implemented according to the SAP version 1.0, dated xx.xx.xxxx.

The present results are built on *sham randomisation* generated from the most recent export from Viedoc. No true treatment assignments have been unlocked. All findings in this document should therefore be interpreted as preliminary and descriptive only. Final efficacy comparisons will not be conducted until the database is locked and genuine randomisation codes are used.

<!--
Database was locked on xx.xx.xxxx. The present results are based on the real treatment allocation.
-->


# Patient enrolment and disposition 

There are 360 randomised participants: 27 from Haukeland, 333 from OUS. The FAS includes all participants. 

<!--
## Trial population 

The following table summarizes the number of participants that were screened (?), that were eligible and randomized, that received the treatment and that were lost to follow-up, as well as the number of participants included in the analyses. This table should be used to fill in the CONSORT diagram (??). 

```{r}
# consort_tab %>% 
#   head(10) %>%
#   kable(
#     caption = "Trial population",
#     digits = 2
#   )
tt <- flextable(consort_tab)
autofit(tt) %>%
  set_header_labels(values=list(row_label=" ")) %>%
  set_caption(caption = "Counts")
```
-->

## Patient disposition (reasons for non-completion)


```{r}
body_tab <- body_tab %>% mutate(Total=DOAC+ASA)
tt <- flextable(body_tab)
tt %>%
  colformat_char(j = 1, na_str="NA") %>%
  flextable::compose(
    i = c(3:4,6:10),
    j = "row_label",
    value = as_paragraph("\t", row_label)) %>%
  flextable::compose(
    i = c(1:2,5),
    j = "row_label",
    value = as_paragraph(as_b(row_label))) %>%
  set_header_labels(values=list(row_label=" ")) %>%
  autofit() %>%
  set_caption(caption = "Overview of study completion and reasons for non-completion")
```

<!--
## Timing of end of study, withdrawals and follow ups


Time from randomisation to end of study and time from randomisation to withdrawal/lost to follow-up is summarized by median and min-max, overall and by treatment group. 

```{r}
tt <- flextable(time_tab)
tt %>%
  set_header_labels(values=list(dsc=" ")) %>%
  autofit() %>%
  set_caption(caption = "Length of study by treatment groups")
```
-->

## Protocol deviations

Number of major and minor protocol deviations, summarized by treatment group with details of type of deviation provided. 

```{r}
tt <- flextable(minorPD)
tt %>%
  set_header_labels(values=list(ran_trt="Treatment",cat="Category of PD")) %>%
  autofit() %>%
  set_caption(caption = "Number of minor protocol deviations")
```

There are currently no protocol deviations that are categorised as "major".

<!--
```{r}
tt <- flextable(majorPD)
tt %>%
  set_header_labels(values=list(ran_trt="Treatment",cat="Category of PD")) %>%
  autofit() %>%
  set_caption(caption = "Number of major protocol deviations")
```


## Adherence to allocated treatment 


Number of participants participants switching between ASA and DOAC or stopping the treatment altogether (so far - final data could reveal more switches), by treatment group and in total.

```{r}
tt <- flextable(adh_tab)
tt %>%
  set_header_labels(values=list(ran_trt=" ",n_noChange="No change in study drug",
                                n_switch_stop="Switching or stopping")) %>%
  autofit() %>%
  set_caption(caption = "Number of participants switching or stopping.")
```

-->



<!--
The SAS is the same as the FAS.
The PP includes all participants except 
-- non-completers that did not die (voluntary discontinuation mostly)
-- participants with important protocol deviations
-- participants switching between ASA and DOAC or stopping the treatment altogether.


```{r}
tt <- flextable(set_tab)
tt %>%
  set_header_labels(values=list(ran_trt=" ",FAS="Full analysis set",PP="Per protocol set")) %>%
  autofit() %>%
  set_caption(caption = "Number of participants in the different analysis sets.")
```
-->

# Demographics and baseline characteristics


## Table 1


```{r}
tt <- flextable(dm_table_abs)
tt %>% 
  set_header_labels(values=list(text=" ","1"=" ")) %>%
  autofit() %>%
  set_caption(caption = "Baseline characteristics for all 360 participants. Continuous variables are summarised by mean (SD), or by median (IQR) as appopriate.",align_with_table = FALSE)
```


## Demographics and medical history

```{r}
indent <- c(3:4,6:7,9:10,12:13,15:16,18:19,21:22,24:27)
notindent <- which(!1:27 %in% indent)
tt <- flextable(dm_baseline)
tt %>%
  flextable::compose(
    i = indent,
    j = "Characteristic",
    value = as_paragraph("\t", Characteristic)) %>%
  flextable::compose(
    i = notindent,
    j = "Characteristic",
    value = as_paragraph(as_b(Characteristic)))  %>%
  autofit() %>%
  set_caption(caption = "Demographics and medical history.",
              align_with_table = FALSE)
```

## Vital signs and physical characteristics at baseline


```{r}
indent <- c(10:12,14:16,18:21)
notindent <- which(!1:21 %in% indent)
tt <- flextable(ph_tab)
tt %>%
  flextable::compose(
    i = indent,
    j = "Characteristic",
    value = as_paragraph("\t", Characteristic)) %>%
  flextable::compose(
    i = notindent,
    j = "Characteristic",
    value = as_paragraph(as_b(Characteristic)))  %>%
  autofit() %>%
  set_caption(caption = "Vital signs and physical characteristics at baseline.",
              align_with_table = FALSE)
```


## Clinical chemistry and hematology at baseline

```{r}
indent <- c(14,20,22)
notindent <- which(!1:23 %in% indent)
tt <- flextable(om_baseline)
tt %>% flextable::compose(
    i = indent,
    j = "Characteristic",
    value = as_paragraph("\t", Characteristic))  %>%
  autofit() %>%
  set_caption(caption = "Some results related to clinical chemistry and hematology at baseline.",align_with_table = FALSE)
```


## Echocardiography pre-TAVI and at baseline



```{r}
tt <- flextable(eco_screening)
tt  %>%
  autofit() %>%
  set_caption(caption = "Some echocardiography parameters pre-TAVI.",align_with_table = FALSE)
```

```{r}
tt <- flextable(eco_baseline)
tt  %>%
  autofit() %>%
  set_caption(caption = "Some echocardiography parameters at baseline (post-TAVI).",align_with_table = FALSE)
```

<!--
## Characteristics of the TAVI procedure

```{r}
indent <- c(2:3,5:6,8:9,11)
notindent <- which(!1:11 %in% indent)
tt <- flextable(tavi_baseline)
tt %>% flextable::compose(
    i = indent,
    j = "Characteristic",
    value = as_paragraph("\t", Characteristic)) %>%
  flextable::compose(
    i = notindent,
    j = "Characteristic",
    value = as_paragraph(as_b(Characteristic)))  %>%
  autofit() %>%
  set_caption(caption = "Characteristics of the TAVI procedure.",align_with_table = FALSE)
```
-->

# Primary analyses of primary endpoints

## Co-primary efficacy endpoint (HALT)

### Descriptive statistics


```{r}
load("data/res/prim_eff_tab.RData")
indent <- c(5:9)
notindent <- which(!1:9 %in% indent)
tt <- flextable(effsum2)
tt %>%
  set_header_labels(values=list(cthalt=" ")) %>% 
  flextable::compose(
    i = indent,
    j = "cthalt",
    value = as_paragraph("\t", cthalt)) %>%
  flextable::compose(
    i = notindent,
    j = "cthalt",
    value = as_paragraph(as_b(cthalt)))  %>%
  autofit() %>%
  set_caption(caption = "Descriptive statistics for HALT (primary efficacy endpoint). Counts and proportions.",align_with_table = FALSE)
```

### Unadjusted analysis with multiple imputation

The analysis model only uses the treatment variable and no other covariates.

Multiple imputation with imputation model containing BMI, sodium, potassium,
ALT, triglycerides, albumin, and bilirubin.


```{r}
halt_main_ratio$contrast <- "DOAC / ASA"
tt <- flextable(halt_main_ratio[,c("contrast","estimate","p.value",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average unadjusted risk ratio, along with corresponding p-value and confidence interval.",align_with_table = FALSE)
```


```{asis, echo=(halt_main_ratio$p.value<0.05)}
We see from the table above that the null hypothesis of equality is rejected.
```

```{asis, echo=(halt_main_ratio$p.value>=0.05)}
We see from the table above that the null hypothesis of equality is not rejected.
```


```{r}
tt <- flextable(halt_main_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average unadjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```


## Co-primary safety endpoint

### Descriptive statistics


```{r}
load("data/res/prim_saf_fig.RData")
load("data/res/prim_saf_tab.RData")
indent <- c(4:7)
notindent <- which(!1:7 %in% indent)
tt <- flextable(safsum)
tt %>%
  set_header_labels(values=list(event_type=" ")) %>% 
  flextable::compose(
    i = indent,
    j = "event_type",
    value = as_paragraph("\t", event_type)) %>%
  flextable::compose(
    i=notindent,
    j = "event_type",
    value = as_paragraph(as_b(event_type)))  %>%
  autofit() %>%
  set_caption(caption = "Descriptive statistics for primary safety endpoint. Counts and proportions. The counts are the number of participants experiencing an event of a particular type as their *first* safety event. Some participants may experience more than one safety event.",align_with_table = FALSE)
```


**Occurrence and timing of intercurrent events**

Out of 360 participants, `r saf_events$n_deviations` participants experience some form of treatment deviation, mostly switching between the two study drugs. All participants have the possibility to switch between study drugs. A few participants switch multiple times.

```{r}
tt <- flextable(dev_tab)
tt %>%
  set_header_labels(values=list(ran_trt=" ",n_noChange="No change in study drug",
                                n_switch_stop="Switching or stopping",
                                n_early_disc="Early discontinuation")) %>%
  autofit() %>%
  set_caption(caption = "Number of participants with treatment deviations.")
```

Out of the `r saf_events$total` safety events, `r saf_events$saf_switch` happen in participants that also switch between the treatments at some point. Among these  `r saf_events$saf_switch` participants:  `r saf_events$before` experience the safety event before switching, while  `r saf_events$after` experience the safety event after their first switch.


```{r switchingSafetyfig, echo = FALSE, fig.path="markdown_figs/" , fig.width = 12, fig.height=8, fig.cap="Timing of safety events and/or treatment deviations. Some participants switch between drugs multiple times and in those cases the figure gives the timing of the first switch."}
load("data/res/prim_saf_fig.RData")
selected
```


In this figure there are `r saf_events$n_dev_plus_saf` participants, including `r saf_events$total` participants experiencing the safety event, and `r saf_events$n_deviations` participants with treatment deviations (`r saf_events$saf_switch` participants are part of both groups).


### Adjusted analysis with multiple imputation, treatment policy strategy

Covariates in the analysis model: treatment, age, sex, cad, prev_stroke, diabetes, hypertension, GFR

Multiple imputation with imputation model containing the same covariates.

```{r}
tt <- flextable(safety_main_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{asis, echo=(safety_main_diff$conf.high<0.119)}
We see from the table above that the null hypothesis of inferiority is rejected.
```

```{asis, echo=(safety_main_diff$conf.high>=0.119)}
We see from the table above that the null hypothesis of inferiority is not rejected.
```

```{r}
safety_main_ratio$contrast <- "DOAC / ASA"
tt <- flextable(safety_main_ratio[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```


## Overall conclusions

```{asis, echo=(halt_main_ratio$p.value<0.05 & safety_main_diff$conf.high<0.119 & halt_main_ratio$estimate>1)}
Both hypotheses are rejected, but DOAC appears to be inferior wrt HALT. Check!
```

```{asis, echo=(halt_main_ratio$p.value>=0.05 | safety_main_diff$conf.high>=0.119)}
Study is inconclusive.
```

```{asis, echo=(halt_main_ratio$p.value<0.05 & safety_main_diff$conf.high<0.119 & halt_main_ratio$estimate<1)}
* DOAC is superior to ASA with respect to the probability of experiencing HALT.
* DOAC is non-inferior to ASA with respect to the probability of experiencing a safety event.
```


```{r primaryfig, echo = FALSE, fig.path="markdown_figs/" , fig.width = 12, fig.height=6, fig.cap="Summary of primary analyses."}
ggarrange(haltplot,safetyplot,ncol=2,nrow=1)
```

# Sensitivity analyses of primary endpoints

## HALT

```{r}
eff_sens_ratio <- rbind(halt_main_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens1_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens2_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens3_ratio[,c("contrast","estimate","conf.low","conf.high")])
eff_sens_ratio$contrast <- c("primary analysis","1: adjusted, with MI","2: unadjusted, complete-case","3: unadjusted, worst-case")
tt <- flextable(eff_sens_ratio)
tt %>%
  set_header_labels(values=list(contrast=" ",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Co-primary efficacy: results of primary analysis and 3 sensitivity analyses. Estimated average risk ratios, along with corresponding confidence intervals. MI stands for Mulitple Imputation.",align_with_table = FALSE)
```


```{r}
eff_sens_diff <- rbind(halt_main_diff[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens1_diff[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens2_diff[,c("contrast","estimate","conf.low","conf.high")],
                       halt_sens3_diff[,c("contrast","estimate","conf.low","conf.high")])
eff_sens_diff$contrast <- c("primary analysis","1: adjusted, with MI","2: unadjusted, complete-case","3: unadjusted, worst-case")
tt <- flextable(eff_sens_diff)
tt %>%
  set_header_labels(values=list(contrast=" ",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Co-primary efficacy: results of primary analysis and 3 sensitivity analyses. Estimated average risk differences, along with corresponding confidence intervals. MI stands for Mulitple Imputation.",align_with_table = FALSE)
```


## Safety composite


```{r}
saf_sens_diff <- rbind(safety_main_diff[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens1_diff[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens2_diff[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens3_diff[,c("contrast","estimate","conf.low","conf.high")])
saf_sens_diff$contrast <- c("primary analysis","1: unadjusted, with MI","2: adjusted, complete-case","3: adjusted, worst-case")
tt <- flextable(saf_sens_diff)
tt %>%
  set_header_labels(values=list(contrast=" ",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Co-primary safety: results of primary analysis and 3 sensitivity analyses. Estimated average risk differences, along with corresponding confidence intervals. MI stands for Mulitple Imputation.",align_with_table = FALSE)
```

```{r}
saf_sens_ratio <- rbind(safety_main_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens1_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens2_ratio[,c("contrast","estimate","conf.low","conf.high")],
                       safety_sens3_ratio[,c("contrast","estimate","conf.low","conf.high")])
saf_sens_ratio$contrast <- c("primary analysis","1: unadjusted, with MI","2: adjusted, complete-case","3: adjusted, worst-case")
tt <- flextable(saf_sens_ratio)
tt %>%
  set_header_labels(values=list(contrast=" ",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Co-primary safety: results of primary analysis and 3 sensitivity analyses. Estimated average risk ratios, along with corresponding confidence intervals. MI stands for Mulitple Imputation.",align_with_table = FALSE)
```

<!--
```{asis, echo=(safety_main_ratio$conf.high<1.35)}
For the fourth sensitivity analysis we re-do the non-inferiority hypothesis test, but using the risk ratio and a non-inferiority margin of 1.35. We see from the table above that this null hypothesis of inferiority is rejected.
```

```{asis, echo=(safety_main_ratio$conf.high>=1.35)}
For the fourth sensitivity analysis we re-do the non-inferiority hypothesis test, but using the risk ratio and a non-inferiority margin of 1.35. We see from the table above that this null hypothesis of inferiority is not rejected.
```
-->

# Supplementary analyses of primary endpoints

## HALT: hypothetical strategy for death

The analysis model only uses the treatment variable and no other covariates.

Multiple imputation with imputation model containing BMI, sodium, potassium,
ALT, triglycerides, albumin, and bilirubin.


```{r}
load("data/res/prim_eff_supp_tab.RData")
halt_supp_ratio$contrast <- "DOAC / ASA"
tt <- flextable(halt_supp_ratio[,c("contrast","estimate","p.value",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average unadjusted risk ratio, along with corresponding p-value and confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(halt_supp_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average unadjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```



## Safety compositet: composite strategy for treatment deviations

```{r}
load("data/res/prim_saf_supp2_tab.RData")
```

With this strategy we still have 360 observations, but now we have `r sums_supp$n_events2` safety events.

```{r}
tt <- flextable(safety_supp2_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
safety_supp2_ratio$contrast <- "DOAC / ASA"
tt <- flextable(safety_supp2_ratio[,c("contrast","estimate","p.value",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk ratio, along with corresponding p-value and confidence interval.",align_with_table = FALSE)
```





## Safety composite: primary strata strategy for treatment deviations

With this strategy we now have `r sums_supp$n3` observations and `r sums_supp$n_events3` safety events.


```{r}
tt <- flextable(safety_supp3_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
safety_supp3_ratio$contrast <- "DOAC / ASA"
tt <- flextable(safety_supp3_ratio[,c("contrast","estimate","p.value",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk ratio, along with corresponding p-value and confidence interval.",align_with_table = FALSE)
```


# Key secondary endpoints

## Clinical efficacy

```{r}
load("data/res/key_sec_tab.RData")
indent <- c(3:6)
notindent <- which(!1:8 %in% indent)
tt <- flextable(ceT[2:9,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))  %>% 
  flextable::compose(
    i = indent,
    j = "at",
    value = as_paragraph("\t", at)) %>%
  flextable::compose(
    i = notindent,
    j = "at",
    value = as_paragraph(at)) %>% 
  autofit() %>%
  set_caption(caption = "Descriptive statistics for clinical efficacy composite by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```

```{r}
tt <- flextable(ce_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
ce_ratio$contrast <- "DOAC / ASA"
tt <- flextable(ce_ratio[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

## Thromboembolic events

```{r}
tt <- flextable(thrT[2:5,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))  %>% 
  autofit() %>%
  set_caption(caption = "Descriptive statistics for thromboembolic events by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```

```{r}
tt <- flextable(thr_diff_ne)
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

## Bleeding events

```{r}
indent <- c(4:7)
notindent <- which(!1:8 %in% indent)
tt <- flextable(varcT[2:9,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))   %>% 
  flextable::compose(
    i = indent,
    j = "at",
    value = as_paragraph("\t", at)) %>%
  flextable::compose(
    i = notindent,
    j = "at",
    value = as_paragraph(at)) %>% 
  autofit() %>%
  set_caption(caption = "Descriptive statistics for VARC-3 bleeding events by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```

```{r}
tt <- flextable(varc_diff_ne)
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```


## All-cause mortality

```{r}
indent <- c(4)
notindent <- which(!1:5 %in% indent)
tt <- flextable(deathT[2:6,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))  %>% 
  flextable::compose(
    i = indent,
    j = "at",
    value = as_paragraph("\t", at)) %>%
  flextable::compose(
    i = notindent,
    j = "at",
    value = as_paragraph(at)) %>%  
  autofit() %>%
  set_caption(caption = "Descriptive statistics for deaths by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```


```{r}
tt <- flextable(dth_diff_ne)
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

## Hemodynamic valve deterioration

```{r}
indent <- c(3,5)
notindent <- which(!1:7 %in% indent)
tt <- flextable(hvdT[2:8,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))  %>% 
  flextable::compose(
    i = indent,
    j = "at",
    value = as_paragraph("\t", at)) %>%
  flextable::compose(
    i = notindent,
    j = "at",
    value = as_paragraph(at)) %>%   
  autofit() %>%
  set_caption(caption = "Descriptive statistics for HVD by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```

As, we see in the table above, no participant has HVD of stage 3.


```{r}
tt <- flextable(hvd_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
hvd_ratio$contrast <- "DOAC / ASA"
tt <- flextable(hvd_ratio[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```


## Safety composite with TIA

```{r}
indent <- c(4:8)
notindent <- which(!1:9 %in% indent)
tt <- flextable(saf2T[2:10,])
tt %>%
  set_header_labels(values=list(at=" ",V1="DOAC",V2="ASA",V3="Overall"))  %>% 
  flextable::compose(
    i = indent,
    j = "at",
    value = as_paragraph("\t", at)) %>%
  flextable::compose(
    i = notindent,
    j = "at",
    value = as_paragraph(at)) %>%   
  autofit() %>%
  set_caption(caption = "Descriptive statistics for safety composite including TIA by treatment arms and overall. Counts and proportions.",align_with_table = FALSE)
```



```{r}
tt <- flextable(saf2_diff[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
saf2_ratio$contrast <- "DOAC / ASA"
tt <- flextable(saf2_ratio[,c("contrast","estimate","conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 2:4, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Estimated average adjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

# Secondary safety endpoints

# Sub-group analyses

## HALT

These analyses use the treatment variable, the subgroup factor, their interaction, and no other covariates.

Multiple imputation with imputation model containing BMI, sodium, potassium,
ALT, triglycerides, albumin, and bilirubin.


```{r subgroupsHALT,echo = FALSE,fig.path="markdown_figs/",warning=FALSE,message=FALSE, fig.width = 20, fig.height=12, fig.cap="Forest plot of subgroup analyses for HALT."}
load("data/res/subgroups_prim_eff_tab.RData")
HALTsubgroups
```

Subgroups with few participants may get confidence intervals which are too wide to show in the figure above. In those case, check the tables below.

```{r}
halt_sub1$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub1[,c("contrast","ageF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(ageF="age",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Age subgroups and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```


```{r}
halt_sub2$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub2[,c("contrast","sex","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Sex and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub3$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub3[,c("contrast","diabetesF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(diabetesF="diabetes",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Diabetes and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub4$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub4[,c("contrast","hypertensionF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(hypertensionF="hypertension",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Hypertension and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub5$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub5[,c("contrast","renal_function","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( renal_function="renal function",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Renal function and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub6$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub6[,c("contrast","valve_type","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( valve_type="valve type",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Valve type and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub7$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub7[,c("contrast","pdF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( pdF="post-dilatation",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Post-dilatation and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub8$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub8[,c("contrast","ascF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( ascF="ascending aorta diam.",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Ascending aorta diameter and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
halt_sub9$contrast <- "DOAC / ASA"
tt <- flextable(halt_sub9[,c("contrast","frailty_status","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( frailty_status="frailty index",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Frailty and HALT. Estimated average unadjusted risk ratio, along with corresponding confidence interval.",align_with_table = FALSE)
```

## Safety composite


These analyses use the treatment variable, the subgroup factor, their interaction, and covariates age, sex, cad, prev_stroke, diabetes, hypertension, GFR.

Multiple imputation with imputation model containing treatment, age, sex, cad, prev_stroke, diabetes, hypertension, GFR.


```{r subgroupsSAF,echo = FALSE,fig.path="markdown_figs/",warning=FALSE,message=FALSE, fig.width = 20, fig.height=12, fig.cap="Forest plot of subgroup analyses for safety composite."}
load("data/res/subgroups_prim_saf_tab.RData")
SAFsubgroups
```

Subgroups with few participants may get confidence intervals which are too wide to show in the figure above. In those case, check the tables below.

```{r}
tt <- flextable(saf_sub1[,c("contrast","ageF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(ageF="age",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Age subgroups and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```


```{r}
tt <- flextable(saf_sub2[,c("contrast","sex","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Sex and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub3[,c("contrast","diabetesF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(diabetesF="diabetes",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Diabetes and safety risk. Estimated average adjusted risk difference, along with correspondin confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub4[,c("contrast","hypertensionF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list(hypertensionF="hypertension",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Hypertension and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub5[,c("contrast","renal_function","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( renal_function="renal function",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Renal function and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub6[,c("contrast","valve_type","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( valve_type="valve type",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Valve type and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub7[,c("contrast","pdF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( pdF="post-dilatation",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Post-dilatation and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub8[,c("contrast","ascF","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( ascF="ascending aorta diam.",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Ascending aorta diameter and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

```{r}
tt <- flextable(saf_sub9[,c("contrast","frailty_status","estimate",
                            "conf.low","conf.high")])
tt %>%
  set_header_labels(values=list( frailty_status="frailty index",conf.low="95CI_low",conf.high="95CI_high")) %>% 
  colformat_double(j = 3:5, digits = 3) %>%
  autofit() %>%
  set_caption(caption = "Frailty and safety risk. Estimated average adjusted risk difference, along with corresponding confidence interval.",align_with_table = FALSE)
```

# Additional safety analysis


## Overview of adverse events, serious adverse events and suspected unexpected serious adverse reaction


```{r}
load("data/res/ae_tab.RData")
tt <- flextable(ae_table)
tt %>%
  set_header_labels(values=list(text=" "))  %>%
  autofit() %>%
  set_caption(caption = "Summary of adverse events.",align_with_table = FALSE)
```

There are no SUSARs in the dataset. No SAE which is unexpected and possibly, probably or definitely related to study medication.

<!--
## Suspected adverse reactions: AEs and SAEs with a possible, probable or definite relation to study treatments


```{r}
tt <- flextable(pae_table)
tt %>%
  set_header_labels(values=list(text=" "))  %>%
  autofit() %>%
  set_caption(caption = "Summary of adverse events with a possible, probable or definite relation to study treatments.",align_with_table = FALSE)
```

There are no SUSARs in the dataset.
-->

## Adverse Events by System Organ Class and Preferred term 

```{r}
tt <- flextable(ae_sum)
tt %>%
  add_header_row(values=c(" ","AE","SAE"),colwidths = c(2,2,2),top=T)  %>%
  set_header_labels(values=list(soc="System organ class",pt="Preferred term","0_DOAC"="DOAC",
                                "0_ASA"="ASA","1_DOAC"="DOAC","1_ASA"="ASA"))  %>%
  autofit() %>% theme_box %>%
  set_caption(caption = "Number of AEs and SAEs by system organ class and preferred term.",align_with_table = FALSE)
```